---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

First of all, let's read in the data.  Note that we're assuming the CSV file is in our working directory.

```{r}
setwd("~/Bluefin/R Working Directory/represearchproj1")
activitydata <- read.csv(unz("activity.zip", "activity.csv"))
```

Next, we want to convert the date field, which is stored as text, to be of the R "date" type.

```{r}
activitydata$date <- as.Date(activitydata$date,"%Y-%m-%d")
```

## What is mean total number of steps taken per day?


Now, use ddply to get the number of steps by day.  Of course, we'll have to use the plyr library for this.

```{r}
library(plyr)
activitybyday <- ddply(activitydata,~date,summarise,tot=sum(steps,na.rm=TRUE))
mean1 <- mean(activitybyday$tot)
median1 <- median(activitybyday$tot)
```

The following histogram shows the distribution of the number of steps taken in a day.

```{r}
hist(activitybyday$tot,breaks=20, col="lightblue", main="Histogram of Steps Taken per Day", xlab="Number of Steps")
```

Now we're going to get the mean and the median.

```{r}
mean1 <- mean(activitybyday$tot)
median1 <- median(activitybyday$tot)
```

The mean number of steps taken per day is  `r mean1`.
The median number of steps taken per day is  `r median1`.



## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
